Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-22 main.tex
linear

% *** PACKAGES *** %

\usepackage{xifthen}
\usepackage[utf8]{inputenc}
\usepackage{dashbox}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
\usepackage{virginialake}
\vlstemheight=12pt

@@

@@

>>>>

% *** PACKAGES *** %
%\usepackage{fdsymbol}

\usepackage{xifthen}
\usepackage[utf8]{inputenc}
\usepackage{dashbox}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
%\usepackage{stmaryrd}
\usepackage{virginialake}
\vlstemheight=12pt

@@

\newcommand{\frameof}[1]{#1^\star}

@@

Now we are going to show how from a given fonet
$\tuple{\gC,\linkingof\gC}$ we can construct a sequent proof $\Pi$ in
$\FOMLL$ such that $\fographof\Pi=\tuple{\gC,\linkingof\gC}$. In the
proof net literature, this operation is also called
\emph{sequentialization}. The basic idea behind our sequentialization
is to construct a proposional linked cograph, called the \bfit{frame}~\cite{hughes:unifn}
of $\gC$, in which the dependencies between the binders in $\gC$ are
encoded as links. Then we can apply the \emph{splitting tensor
theorem} to the frame, and then reconstruct the sequent proof $\Pi$.

More formally, let $\Gamma$ be a sequent with $\graphof\Gamma=\gC$, to which we
exhaustively apply the following
subformula rewriting steps, to obtain a sequent $\frameof\Gamma$:
\begin{enumerate}
\item {\bf Encode dependencies as fresh links.} For each dependency
  $\pair{\single x,\single y}$ in $\gC$, with corresponding
  subformulas $\exists x A$ and $\forall y B$ in $\Gamma$, we pick a
  fresh (nullary) predicate symbol $q$, and then replace $\exists
  x. A$ by $q \cand \exists x. A$, and replace $\forall y. B$ by
  $\dual q \cor \forall y. B$.
\item {\bf Erase quantifiers.} After step 1, remove all the
  quantifiers, i.e., replace $\exists x.A$ by $A$ and replace $\forall
  y.B$ by $B$ everywhere.
\item {\bf Simplify atoms.} After step 2, replace every predicate
  $p(t_1 \cdots t_n)$ (resp. $\dual p(t_1 \cdots t_n)$) with a nullary
  predicate symbol $p$ (resp.~$\dual p$)
\end{enumerate}
The $\linkingof{\frameof\Gamma}$ consists of the pairs induced by
$\linkingof\gC$ and the new pairs $\set{q,\dual q}$ introduced in
step~1 above.  Now we define the \bfit{frame} of $\gC$, denoted
$\frameof\gC$, as
$\tuple{\graphof{\frameof\Gamma},\linkingof{\frameof\Gamma}}$.

\begin{lemma}\label{lem:frame}
  A linked fograph $\gC$ induces a bimatching iff its frame $\frameof\gC$ induces a bimatching.
\end{lemma}

Note that the linking $\lambda_m$ is a valid $\MLLm$ proof net.

We define the \bfit{frame} of a linked fograph to be the linked cograph defined as follows:
